\documentclass[titlepage]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{tikz}
\pagestyle{fancy}
\fancyhead[L]{\thepage}
\title{\huge Computer Workshop\\Final Assignment}
\author{Morteza Javadian\\ID: 402521162}
\date{Date: 4 Bahman, 1402}

\begin{document}
	
	\maketitle
	
	\renewcommand{\contentsname }{ TABLE OF CONTENTS}
	
	\tableofcontents
	\addtocontents{toc}{~\hfill  Page\par}
	\let\LaTeXStandardTableOfContents\tableofcontents
	
	\renewcommand{\tableofcontents}
	{
		\begingroup
		\renewcommand{\bfseries}{\relax}
		\LaTeXStandardTableOfContents
		\endgroup
	}

	\newpage
	\fancyhead[R]{\textit{Assignments}}
	
	\section{Git and GitHub}
	\subsection{Repository Initialization and Commits}
	Write about how you set up the repository for this assignment. Explain every step in detail.
	
	first I made a new repository wiht ReadMe in my github and clone it in my coumputer. then I added .github/workflow and main.tex to my repository folder. then commit this changes and tagging my repository. finally I push commit and tags to my github. Note that the tag isn't push with commit and must puah separating tag to github.
	
	\subsection{GitHub Actions for LaTeX Compilation}
	Provide a walkthrough of setting up GitHub Actions to automatically compile your LaTeX document and any challenges you encountered.
	
	
	
	
	
	\section{Exploration Tasks}
	\subsection{Vim Advanced Features}
	Explore and document 3 advanced features of Vim that were not covered in class.
	\newline
	1. gJ – merge the line below to the current one with no space in between them
	\newline
	2. :b#  – move to the specified buffer (by number)
	\newline
	3. #G / #gg / :# – move to a specified line number (replace # with the line number)
	
	\subsection{Memory profiling}
	\subsubsection{Memory Leak}
	In short, explain what memory leaks are and how they might happen in your program.
	
	Memory leaks occur when a computer program reserves memory for certain operations but fails to release that memory after it is no longer needed. This can eventually lead to poor performance or even program failure due to the lack of memory resources. It's important for developers to carefully manage memory allocation and deallocation in their programs to avoid memory leaks.
	
	\subsubsection{Memory profilers}
	Read about a tool called \textit{Valgrind} and write about their purpose and how it helps when memory leaks happen.
	
	Memory leaks happen when a program allocates memory but fails to release it properly, leading to a gradual consumption of memory that can eventually cause the program to crash or run out of memory. Valgrind's memory leak detection tools can track memory allocations and deallocations, identify where memory was allocated and where it was lost, and provide detailed reports to help developers pinpoint and fix these issues. This can be instrumental in improving the stability and reliability of software. 
	
	
	
	
	
	
\end{document}